{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-07-11 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
good night

\subsection{Explaining the Distance decay effects with the gravity model}
The results of strongly connected urban regions in the form of communities in the mobility network of Twitter user spatial interactions yield geographically cohesive, non-overlapping urban areas. 
While it provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain, the reasons on why they are geographically cohesive and non-overlapping or why the boundaries stop/emerge at certain spatial extend that leads to different size of the urban areas are not clear. 
As the depicted urban boundaries exhibited a strong instance of spatial proximity, we adopt the gravity model (Eq. \eqref{eq:3}) to explain how distance decay effects found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas.

In this case, the distance between two derived urban areas is measured by the geodetic distance between the centroid locations of the two.

@@

\clearpage
\section{Conclusion and Discussion}
Talk about interplay between human mobility

In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in Great Britain. 
Twitter user movements were used to establish a connectivity network of the fishnet cells.
Then we applied the map equation algorithm to partition the network and associated geographic regions.
The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries in Great Britain.
By performing a statistical analysis of Twitter user mobility patterns in Great Britain, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in Great Britain.

@@

The purpose of trip
contextualizing

>>>>

\subsection{Explaining the Distance decay effects with the gravity model}
The results of strongly connected urban regions in the form of communities in the mobility network of Twitter user spatial interactions yield geographically cohesive, non-overlapping urban areas. 
While it provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain, the reasons on why they are geographically cohesive and non-overlapping or why the boundaries stop/emerge at certain spatial extent that leads to different size of the urban areas are not clear. 
As the depicted urban boundaries exhibit a strong instance of spatial proximity, the gravity model is employed (Eq. \eqref{eq:3}) to explain how distance decay effects found in the mobility patterns affect the interaction strength among non-administrative anthropographic urban areas.

In this model, the distance between two derived urban areas is measured by the geodetic distance between the centroid locations of the two.
As it is mentioned above,  $P_{i}$ and $P_{j}$  are the observed interaction between urban area $i$ and $j$, which are measured by the aggregation of movement flux in each urban area.
In particular, we set the distance decay parameter $\beta$ value as 0.8: (1) As we hypothesize that the distance decay parameters found in the underlying mobility patterns potentially contribute to $\beta$ in the gravity model (2) and we have chosen the 10-km cell size based on the collective Twitter user mobility pattern regarding radius of gyration, where the distance decay parameter is 0.8 when radius of gyration $r_{g} > 10 km$ (Fig.~\ref{S4_Fig}(c)).
We found that the gravity model indicates strong linear correlation between the observed versus the estimated interaction strength with $R^{2}$ = 0.89 and $p-value < 0.01$.
This confirms that the depicted urban areas are results of spatial proximity effects, where the strength of human (in this case, Twitter user) spatial interaction between two urban regions decreases as the geographic distance between them increases.
More importantly, since we have used a mobility network to delineate the boundaries, the distance decay effects are well related and explained by the underlying mobility patterns.
In return, the well fitted gravity model provides support that the depicted urban areas are not random artifacts but indeed reflect how people move across geographic regions.

@@

\clearpage
\section{Conclusion and Discussion}
In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in Great Britain. 
Twitter user movements were used to establish a connectivity network of the fishnet cells.
Then we applied the map equation algorithm to partition the network and associated geographic regions.
The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries in Great Britain.
By performing a statistical analysis of Twitter user mobility patterns in Great Britain, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in Great Britain.

@@

%Talk about interplay between human mobility 
%The purpose of trip
%contextualizing
